---
title: "2. Script write-up_analysis"
author: "Emily Raubach"
date: "2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## First steps

Load the necessary packages from the library. 

```{r cars, message=FALSE, warning=FALSE}
library("rjson")
library("RCurl")
library("stringr")
library("dplyr")
library("tm")
library("quanteda")
library("devtools")
library("spacyr")
library("purrr")
library("ggplot2")
library("tidytext")

# Install Quanteda dictionaries from GitHub
# devtools::install_github("kbenoit/quanteda.dictionaries")
# devtools::install_github("quanteda/quanteda.corpora")
library("quanteda.corpora")
library("quanteda.dictionaries")
```

Import the combined data file. 

```{R}
# import data
alltexts_clean <- readRDS("df_clean.rds")

# can also load the dataframe with LSD results
alltexts_clean_lsd <- readRDS("alltexts_clean_lsd.rds")

# create a corpus
my_corpus <- corpus(alltexts_clean)
# alternate corpus
# my_corpus <- corpus(alltexts_clean_lsd)

# summary
head(summary(my_corpus))
```

Remove the one independent congress member: (already done in the LSD RDS file)
```{R}
# remove independent member
alltexts_clean <- alltexts_clean[!(alltexts_clean$Party.General %in% c('Independent')),]
```

## Add LIWC data to the dataframe
```{R warning=FALSE}
# Load the csv files
LIWC_Rep <- read.csv2(file = "LIWC_Rep.csv")
LIWC_Dem <- read.csv2(file = "LIWC_Dem.csv")

# Combine the files to create one dataframe
LIWC <- rbind(LIWC_Dem, LIWC_Rep)

# Add the LIWC files to the clean Alltexts file (without LSD analyses)
alltexts_LIWC <- left_join(alltexts_clean, LIWC, by = "Name")

# Save as an RDS file
saveRDS(alltexts_LIWC, file = "alltexts_LIWC.rds")
```

## 1. Complexity
There are four measures that I have included in order to measure the complexity of a text. These are big words (BW), mean sentence length (MSL), lexical density (LD), and type-token ratio (TTR).

# 1.1. Big Words (BW)
To be done using LIWC.

```{R}
# Big words = Sixltr in LIWC
summary(alltexts_LIWC$Sixltr[alltexts_LIWC$Party.General == "Democrat"])
summary(alltexts_LIWC$Sixltr[alltexts_LIWC$Party.General == "Republican"])

# Seems to be more or less identical

# Multiple Linear Regression for big words (BW)
fit <- lm(ipron ~ Party.General + Sex + age + educ + seniority + Region +
            Christian + statevote_2016, 
          data = alltexts_LIWC[alltexts_LIWC$speechcount > 9, ])
# + statevote_2016
# show results
summary(fit)

# Multiple Linear Regression for Positive Emotion with interaction term
fit <- lm(social ~ Party.General + Sex + age + educ + seniority + Region +
            Christian + statevote_2016 + Party.General:Sex, # interaction term 
          data = alltexts_LIWC[alltexts_LIWC$speechcount > 0, ])

```

# 1.2. Mean Sentence Length (MSL)
To be done using LIWC.

```{R}
# Republicans use slightly longer sentences? WPS = words per sentence?
summary(alltexts_LIWC$WPS[alltexts_LIWC$Party.General == "Democrat"])
summary(alltexts_LIWC$WPS[alltexts_LIWC$Party.General == "Republican"])
```

# 1.3. Lexical Density (LD)
LD = % of lexical words = 1 - % of function words 

Lexical words = nouns, names, adjectives, verbs, and adverbs

Function words = determiners, pronouns, prepositions, modal verbs, conjuctions, auxiliary verbs, etc. 


```{R}
# Percentage of function words, higher for Republicans? But not meaningful?
summary(alltexts_LIWC$function.[alltexts_LIWC$Party.General == "Democrat"])
summary(alltexts_LIWC$function.[alltexts_LIWC$Party.General == "Republican"])

```

# 1.4. Type-Token Ratio
The relationship between the vocabulary size and the number of word types.

Vocabulary size / text length
Number of types / number of tokens

```{R}
# Types from after stemming? 

# Tokess from WC (word count)

#alltexts_LIWC$

```

# Tone
LIWC variable Emotional Tone (Tone)
```{R}
# Emotional Tone? 
summary(alltexts_LIWC$Tone[alltexts_LIWC$Party.General == "Democrat"])
summary(alltexts_LIWC$Tone[alltexts_LIWC$Party.General == "Republican"])

# Multiple Linear Regression for Tone
fit <- lm(Tone ~ Party.General + Sex + age + educ + seniority + Region +
            Christian + statevote_2016, 
          data = alltexts_LIWC[alltexts_LIWC$speechcount > 9, ])
# + statevote_2016
# show results
summary(fit)

  ```


## 2. Parts of Speech

# 2.1. Noun Phrases vs. Verb Phrases
Function words vs. ?

```{R}


```


# 2.2. Pronouns
There are a couple of different variables for pronouns, the general one is "pronoun", with specific variables for first person singular/plural, you, etc. 

```{R}
# Percentage of pronoun usage
summary(alltexts_LIWC$pronoun[alltexts_LIWC$Party.General == "Democrat"])
summary(alltexts_LIWC$pronoun[alltexts_LIWC$Party.General == "Republican"])

# ...
 
```

# 2.3. Prepositions
To be done using LIWC.

```{R}
```


## 3. Emotionality

# Lexicoder Sentiment Decoder (LSD)
For the initial analysis of emotionality in the texts I used the Lexicoder Sentiment Decoder from Young and Soroka (2012). LSD is available as add-on to the quanteda package. 

```{R}
# Apply LSD dictionary to my_corpus and save the output to a separate file
output_lsd <- liwcalike(my_corpus, dictionary = data_dictionary_NRC)

# View the first couple of rows
head(output_lsd)
```

```{R}
# Add variables to dataframe
alltexts_clean$anger <- output_lsd$anger
alltexts_clean$positive <- output_lsd$positive
alltexts_clean$negative <- output_lsd$negative
alltexts_clean$fear <- output_lsd$fear
alltexts_clean$joy <- output_lsd$joy
alltexts_clean$disgust <- output_lsd$disgust
alltexts_clean$trust <- output_lsd$trust
alltexts_clean$sadness <- output_lsd$sadness
```

```{R}
# Save dataframe as R file
saveRDS(alltexts_clean, file = "alltexts_clean_lsd.rds")
```

The package sjPlot helps plotting Word output.

```{R}
library('sjPlot')

# compute descriptive statistics
# tab_df(alltexts_clean[,3:5])
```

Descriptive measures of the variables. 

```{R}
library('Hmisc')

vars <- c('Sex','Region','Party.General','Christian','age','seniority',
          'educ','JD_degree','speechcount','anger','positive','negative',
          'fear','joy','disgust','trust')

describe(alltexts_clean[,vars])
```

The correlations between speechcount and measures of emotionality are almost non-existant, which is a good sign for my analysis, it means that the speech count does not affect the emotionality measures. 

```{R}
library('corrplot')

vars_corr <- c('age','seniority','speechcount','anger','positive',
               'negative','fear','joy','disgust','trust')

M <- cor(as.matrix(alltexts_clean[,vars_corr]))

# mat : is a matrix of data
# ... : further arguments to pass to the native R cor.test function
cor.mtest <- function(mat, ...) {
    mat <- as.matrix(mat)
    n <- ncol(mat)
    p.mat<- matrix(NA, n, n)
    diag(p.mat) <- 0
    for (i in 1:(n - 1)) {
        for (j in (i + 1):n) {
            tmp <- cor.test(mat[, i], mat[, j], ...)
            p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
        }
    }
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
  p.mat
}

# matrix of the p-value of the correlation
p.mat <- cor.mtest(as.matrix(alltexts_clean[,vars_corr]))

# Leave blank on no significant coefficient
corrplot(M, type = "upper", order = "hclust", p.mat = p.mat, 
         sig.level = 0.01, insig = "blank")

col <- colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))
corrplot(M, method="color", col=col(200),  
         type="upper", order="hclust", 
         addCoef.col = "black", # Add coefficient of correlation
         tl.col="black", tl.srt=45, #Text label color and rotation
         # Combine with significance
         p.mat = p.mat, sig.level = 0.01, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```

# 3.1. Positive Emotion

```{R}
library(ggthemes)
library(grid)

fill <- "#4271AE"
line <- "#1F3552"

# Boxplot for Postive emotion
p10 <- ggplot(alltexts_clean, aes(x = Party.General, y = positive)) +
        geom_boxplot(fill = fill, colour = line) +
        scale_y_continuous(name = "LSD Positive",
                           breaks = seq(0, 15, 1),
                           limits=c(0, 15)) +
        scale_x_discrete(name = "Party") +
        ggtitle("Title") +
        theme_economist() +
        theme(axis.line.x = element_line(size = 0.5, colour = "black"),
              axis.line.y = element_line(size = 0.5, colour = "black"),
              legend.position = "bottom", legend.direction = "horizontal",
              legend.box = "horizontal",
              legend.key.size = unit(1, "cm"),
              plot.title = element_text(family="Tahoma"),
              text = element_text(family = "Tahoma"),
              axis.title = element_text(size = 12),
              legend.text = element_text(size = 9),
              legend.title=element_text(face = "bold", size = 9))

# View plot (best if enterest in the console)
p10



# Boxplot for both Positive and Negative emotion
df1 <- alltexts_clean[,c('Party.General','positive')]
df2 <- alltexts_clean[,c('Party.General','negative')]

colnames(df1) <- c('party','value')
colnames(df2) <- c('party','value')

df1$score <- 'positive'
df2$score <- 'negative'

df <- rbind(df1, df2)

df$score <- factor(df$score)

p11 <- ggplot(df, aes(x = party, y = value)) +
        geom_boxplot(fill = fill, colour = line,
                     alpha = 0.7) +
        scale_y_continuous(name = "Score",
                           breaks = seq(0, 15, 2),
                           limits=c(0, 15)) +
        scale_x_discrete(name = "Party") +
        ggtitle("Boxplot of positive and negative emotion by party") +
        theme_bw() +
        theme(plot.title = element_text(size = 14, family = "Tahoma", face = "bold"),
              text = element_text(size = 12, family = "Tahoma"),
              axis.title = element_text(face="bold"),
              axis.text.x=element_text(size = 11)) +
        facet_grid(. ~ score)
p11

# Boxplot for both Anger and Joy
df1 <- alltexts_clean[,c('Party.General','anger')]
df2 <- alltexts_clean[,c('Party.General','joy')]

colnames(df1) <- c('party','value')
colnames(df2) <- c('party','value')

df1$score <- 'anger'
df2$score <- 'joy'

df <- rbind(df1, df2)

df$score <- factor(df$score)

p12 <- ggplot(df, aes(x = party, y = value)) +
        geom_boxplot(fill = fill, colour = line,
                     alpha = 0.7) +
        scale_y_continuous(name = "Score",
                           breaks = seq(0, 5, 1),
                           limits=c(0, 5)) +
        scale_x_discrete(name = "Party") +
        ggtitle("Boxplot of emotions anger and joy by party") +
        theme_bw() +
        theme(plot.title = element_text(size = 14, family = "Tahoma", face = "bold"),
              text = element_text(size = 12, family = "Tahoma"),
              axis.title = element_text(face="bold"),
              axis.text.x=element_text(size = 11)) +
        facet_grid(. ~ score)
p12

# Boxplot for both Fear and Trust 
df1 <- alltexts_clean[,c('Party.General','fear')]
df2 <- alltexts_clean[,c('Party.General','trust')]

colnames(df1) <- c('party','value')
colnames(df2) <- c('party','value')

df1$score <- 'fear'
df2$score <- 'trust'

df <- rbind(df1, df2)

df$score <- factor(df$score)

p13 <- ggplot(df, aes(x = party, y = value)) +
        geom_boxplot(fill = fill, colour = line,
                     alpha = 0.7) +
        scale_y_continuous(name = "Score",
                           breaks = seq(0, 11, 1),
                           limits=c(0, 11)) +
        scale_x_discrete(name = "Party") +
        ggtitle("Boxplot of emotions fear and trust by party") +
        theme_bw() +
        theme(plot.title = element_text(size = 14, family = "Tahoma", face = "bold"),
              text = element_text(size = 12, family = "Tahoma"),
              axis.title = element_text(face="bold"),
              axis.text.x=element_text(size = 11)) +
        facet_grid(. ~ score)
p13

# Boxplot for both Fear and Trust 
df1 <- alltexts_clean[,c('Party.General','disgust')]
df2 <- alltexts_clean[,c('Party.General','sadness')]

colnames(df1) <- c('party','value')
colnames(df2) <- c('party','value')

df1$score <- 'disgust'
df2$score <- 'sadness'

df <- rbind(df1, df2)

df$score <- factor(df$score)

p14 <- ggplot(df, aes(x = party, y = value)) +
        geom_boxplot(fill = fill, colour = line,
                     alpha = 0.7) +
        scale_y_continuous(name = "Score",
                           breaks = seq(0, 7, 1),
                           limits=c(0, 7)) +
        scale_x_discrete(name = "Party") +
        ggtitle("Boxplot of emotions disgust and sadness by party") +
        theme_bw() +
        theme(plot.title = element_text(size = 14, family = "Tahoma", face = "bold"),
              text = element_text(size = 12, family = "Tahoma"),
              axis.title = element_text(face="bold"),
              axis.text.x=element_text(size = 11)) +
        facet_grid(. ~ score)
p14


# Set color by cond
ggplot(alltexts_clean, aes(x = age, y = positive, color = Party.General)) +
  geom_point(shape = 1)

```

Some remarks with regard to (one-way) ANOVA:
(paraphrase this!)
- two sources of variability in the data: variability within one party and variability between the two parties
- we are interested in the following question: are the differences in the means between the two parties significant or are they due to chance?
- assumptions of ANOVA: errors (residuals) are normally distributed and independent of each other and their variance is constant
- null hypothesis: alphas are zero
- in the case of two groups (Democrats and Republicans), the one-way ANOVA is equivalent to a two-sample t-test
- hence, it might make sense to simply use a t-test
- assumptions t-test: two samples are independent, they can have a different variance, and they are normally distributed
- to be safe, we also perform a non-parametric Mann-Whitney test which is also absolutely significant

```{R}
# mean of positive emotion by party
mean(alltexts_clean$positive[alltexts_clean$Party.General == 'Democratic'])
mean(alltexts_clean$positive[alltexts_clean$Party.General == 'Republican'])

# (one-way) ANOVA
fit <- aov(positive ~ Party.General, data = alltexts_clean)

# show results
summary(fit)

# t-test of two independent samples (Democrats vs. Republcans)
t.test(alltexts_clean$positive ~ alltexts_clean$Party.General, 
       alternative = 'two.sided', conf.level = 0.95)

# QQ plots for Democrats and Republicans
qqnorm(alltexts_clean$positive[alltexts_clean$Party.General == 'Democratic'],
       main = 'Democrats')
qqline(alltexts_clean$positive[alltexts_clean$Party.General == 'Democratic'])

qqnorm(alltexts_clean$positive[alltexts_clean$Party.General == 'Republican'],
       main = 'Republicans')
qqline(alltexts_clean$positive[alltexts_clean$Party.General == 'Republican'])

# independent 2-group Mann-Whitney U Test 
wilcox.test(alltexts_clean$positive ~ alltexts_clean$Party.General)
```

Some remarks with regard to regression analysis:
- variable description table
- summary statistics
- correlation matrix
- regression analysis (multiple models)
- check assumptions (potentially use logarithmic transformtion)
- sensitivity analysis (check interaction effects)

```{R}
# Multiple Linear Regression for Positive Emotion
fit <- lm(negative ~ Party.General + Sex + age + educ + seniority + Region +
            Christian + statevote_2016, 
          data = lsd[lsd$speechcount > 0, ])

# + statevote_2016
# show results
summary(fit)

# Multiple Linear Regression for Positive Emotion with interaction term
fit <- lm(negative ~ Party.General + Sex + age + educ + seniority + Region +
            Christian + Party.General:Sex, # interaction term 
          data = alltexts_clean_lsd[alltexts_clean_lsd$speechcount > 0, ])

```

```{R}
# Scatterplot of most used positive/negative words from LSD
                                                                                                                                                                                                                                                                                                                                                  

```


```{R}
# Diagnostic plots (QQ, et al.)
layout(matrix(c(1,2,3,4), 2, 2))
plot(fit)

# Boxplot for Positive affect
boxplot(positive ~ Party.General,data = alltexts_clean[alltexts_clean$speechcount > 9,], 
        main="Positive Affect", 
        xlab = "Party", ylab = "Positive Affect")
```

# 3.2. Negative Emotion

# Principal Component Analysis

```{R}
#install_github("vqv/ggbiplot")
library("ggbiplot")

df_pca <- prcomp(alltexts_clean[,colnames(alltexts_clean) %in% c("positive", "negative", "anger", "joy", "sadness", "disgust")], center = TRUE,scale. = TRUE)

summary(df_pca)

# Plot PCA
ggbiplot(df_pca)

# basic plot
pcanames <- ggbiplot(df_pca, labels = alltexts_clean$Name)

# without lables
pca_plot <- ggbiplot(df_pca, ellipse=TRUE, obs.scale = .5, var.scale = .5, groups = alltexts_clean$Party.General) +
  scale_colour_manual(name = "Party", values = c("dark blue", "red")) +
  ggtitle("") +
  theme_minimal() +
  theme(legend.position = "bottom")

# with lables
pca_plot <- ggbiplot(df_pca, ellipse=TRUE, obs.scale = .5, var.scale = .5, lables = alltexts_clean$Name, groups = alltexts_clean$Party.General) +
  geom_text(aes(label = alltexts_clean$Name),hjust=0, vjust=0, size = 3) +
  scale_colour_manual(name = "Party", values = c("dark blue", "red")) +
  ggtitle("") +
  theme_minimal() +
  theme(legend.position = "bottom")
  

# Should also include complexity in another version of this plot

```

# 3.3. Anger

```{R}
```

# 3.4. Joy

```{R}
```

# 3.5. Fear

```{R}
```

## Emotion analysis using LIWC

# What do the dictionaries contain?
```{R}
LIWCdic <- readRDS("read_dict_liwc_LIWC2001.rds")

# Should use this to find the words contained in the individual dictionaries?

```

# Messing around
```{r}
table(lsd$Sex, lsd$Party.General, lsd$Christian)
summary(lsd$seniority)
```


```{r}
# POS tagging

spacy_install()
spacy_initialize()
library("spacyr")
library("quanteda")
# create a corpus

lsd_corpus <- corpus(lsd)

summary(lsd_corpus)$Tokens

no_tokens <- ntoken(lsd_corpus)

#spacy_initialize(model = "en")
#lsd_par <- spacy_parse(lsd_corpus, tag = TRUE, pos = TRUE)

head(lsd_par)

# Save created POS tagged file as an RDS file
# saveRDS(lsd_par, "lsd_pos_tagged.rds")

# Load POS tagged file
POS <- readRDS("lsd_pos_tagged.rds")



df1 <- POS[, c("doc_id", "pos")]

df1$ID <- as.integer(gsub('text', '', df1$doc_id))

library(dplyr)

df2 <- group_by(df1, ID) %>%
  summarise(count_verbs = sum(pos == 'VERB'), 
            count_nouns = sum(pos == 'NOUN'), 
            count_pnouns = sum(pos == 'PROPN'))

df2$count_nouns_total <- df2$count_nouns + df2$count_pnouns

df2$no_tokens <- no_tokens

df2$verb <- df2$count_verbs/df2$no_tokens
df2$noun <- df2$count_nouns/df2$no_tokens
df2$noun_total <- df2$count_nouns_total/df2$no_tokens

# add to original LSD file
pos_df <- left_join(lsd, df2[,c('ID','verb','noun','noun_total')], by = 'ID')

#save as RDS file
saveRDS(pos_df,"pos_results.rds")

table(liwc$Region)
```


Correlation plot for LIWC variables
```{r}
# select relevant variables
vars_corr <- c('age','seniority','positive','negative', 'verb', 'noun', 'noun_total')

# create matrix
M <- cor(as.matrix(pos_df[,vars_corr]))

# mat : is a matrix of data
# ... : further arguments to pass to the native R cor.test function
cor.mtest <- function(mat, ...) {
    mat <- as.matrix(mat)
    n <- ncol(mat)
    p.mat<- matrix(NA, n, n)
    diag(p.mat) <- 0
    for (i in 1:(n - 1)) {
        for (j in (i + 1):n) {
            tmp <- cor.test(mat[, i], mat[, j], ...)
            p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
        }
    }
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
  p.mat
}

# matrix of the p-value of the correlation
p.mat <- cor.mtest(as.matrix(pos_df[,vars_corr]))

# define colors
col <- colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))

# create correlation plot
corrplot(M, method="color", col=col(200),  
         type="upper", order="hclust", 
         addCoef.col = "black", # Add coefficient of correlation
         tl.col="black", tl.srt=45, #Text label color and rotation
         # Combine with significance
         p.mat = p.mat, sig.level = 0.01, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)

```


